Toward nonlinear multigrid \\ for nonlinear variational inequalities

### 2023-02-04 talk/slides.tex
will need this ref
bunch of figures from book, and fluid layes problem

\section{obstacle problems, variational inequalities (VIs)}

\section{nonlocal VIs for fluid layers}

\section{what is FAS multigrid?  (for PDEs)}

\section{scalable approaches to VIs}

@@

{\scriptsize
\begin{itemize}
\item T.~Isaac, G.~Stadler, \& O.~Ghattas (2015). \emph{Solution of nonlinear Stokes equations discretized by high-order finite elements on nonconforming and anisotropic meshes, with application to ice sheet dynamics}, SIAM J.~Sci.~Comput.~37 (6), B804--B833, \href{https://doi.org/10.1137/140974407}{10.1137/140974407}
\end{itemize}
}
\end{frame}

>>>>

\section{variational inequalities (VIs) and obstacle problems}

\begin{frame}{the classical obstacle problem}

\begin{center}
\includegraphics[width=0.6\textwidth]{images/obstacle65.pdf}
\end{center}

\begin{frame}{active sets, free boundaries}

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item x
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\includegraphics[width=0.6\textwidth]{images/obstacle-sets.png}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Newton iterations for VIs}

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item x
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\includegraphics[width=\textwidth]{images/vi-newton-gmg-bad.png}

\includegraphics[width=\textwidth]{images/vi-newton-gmg-good.png}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Newton-multigrid for VIs}

xxx
\end{frame}

\begin{frame}{optimality}

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item x
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\includegraphics[width=\textwidth]{images/obstacle-flops-per-n.png}
\end{column}
\end{columns}
\end{frame}

\section{the nonlocal VI for a fluid layer in a climate}

\begin{frame}{problem: fluid layer in a climate}

\begin{center}
\includegraphics[width=0.6\textwidth]{images/fluid-in-climate.png}
\end{center}

\section{FAS multigrid for PDEs}

\section{a possibly scalable approach to nonlocal VIs}

@@

{\tiny
\begin{itemize}
\item[] E.~Bueler (2021). \emph{Conservation laws for free-boundary fluid layers}, SIAM J.~Appl.~Math.~81 (5), 2007--2032, \href{https://doi.org/10.1137/20M135217X}{10.1137/20M135217X}
\item[] E.~Bueler (2021). \emph{PETSc for Partial Differential Equations}, SIAM Press, Philadelphia, PA.
\item[] E.~Bueler (2022). \emph{Performance analysis of high-resolution ice-sheet simulations}, J.~Glaciol., \href{https://doi.org/10.1017/jog.2022.113}{10.1017/jog.2022.113}
\item[] T.~Isaac, G.~Stadler, \& O.~Ghattas (2015). \emph{Solution of nonlinear Stokes equations discretized by high-order finite elements on nonconforming and anisotropic meshes, with application to ice sheet dynamics}, SIAM J.~Sci.~Comput.~37 (6), B804--B833, \href{https://doi.org/10.1137/140974407}{10.1137/140974407}
\end{itemize}
}
\end{frame}
